### 2023-01-24 article.tex
Remove all usages of 'I', except in the last sentence

There are multiple ways of publishing code,
that require increasingly more knowledge to do and result
in increasingly more reproducible experiments:
(1) publishing the code as text only, e.g. by printing
it in a Supplementary Materials, (2) publishing
the code on a hosted website, e.g on GitHub, with
added features (3) publishing 
the installed code within a virtual environment,
for example, using a Singularity container.
Here I will go into details of each of these ways,
by describing some advantages, disadvantages, as well as how to
make the code more FAIR data \cite{wilkinson2016fair}.

@@

It is hard to make raw code be FAIR data. It is hard for computers to find
copy-pasted code in a Supplementary Materials. 
That code is usually only accessible
if the paper has been published under an open access license.
When code can be found and accessed, it is an open question if the
code can \emph{still} interoperate with current datasets, software
and hardware. Raw code usually lacks the metadata to describe its needs.
I would say that raw code, albeit better than no code, fits
FAIR data only poorly.

@@

Hosted code has many additional features, such as
a version-controlled history, continuous integration scripts
and automatically generated metrics.
A code hosting website produces and shares this metadata.
This metadata can help to determine the
reproducibility, correctness and quality of code
of computational experiments.
Here, I discuss those features and why these are important.

@@

Albeit hosted code is vastly superior over raw code
in case of reproduciblity and correctness,
there are some problems with hosted code as well.
The most important one is that hosted code needs maintanance:
the libraries that are used by an experiment
will change over time, inevitably causing the experiment to fail
over time. 
The degradation of software is a known feature for nearly 
four decades (see the definition of 'bit rot' at \cite{steele1983hacker}),
here I will use the more modern (and in this context superior)
definition of software collapse \cite{hinsen2019dealing},
in which software fails due to dependencies on other 
software.
Where that paper recommends using older software foundations 
with multiple implementations \cite{hinsen2019dealing},
this paper recommends a modern solution that potentially has more longevity:
to publish the code installed in a virtual environment
(including the dependencies used at that time), as described below.

>>>>

There are multiple ways of publishing code,
that require increasingly more knowledge to do and result
in increasingly more reproducible experiments:
(1) publishing the code as text only, e.g. by printing
it in a Supplementary Materials, (2) publishing
the code on a hosted website, e.g on GitHub, with
added features (3) publishing 
the installed code within a virtual environment,
for example, using a Singularity container.
In this chapter, details of each of these ways will be described,
including advantages, disadvantages, as well as how to
make the code more FAIR data \cite{wilkinson2016fair}.

@@

It is hard to make raw code be FAIR data. It is hard for computers to find
copy-pasted code in a Supplementary Materials. 
That code is usually only accessible
if the paper has been published under an open access license.
When code can be found and accessed, it is an open question if the
code can \emph{still} interoperate with current datasets, software
and hardware. Raw code usually lacks the metadata to describe its needs.
One could say that raw code, albeit better than no code, fits
FAIR data only poorly.

@@

Hosted code has many additional features, such as
a version-controlled history, continuous integration scripts
and automatically generated metrics.
A code hosting website produces and shares this metadata.
This metadata can help to determine the
reproducibility, correctness and quality of code
of computational experiments.
Below, those features and why these are important are discussed.

@@

Albeit hosted code is vastly superior over raw code
in case of reproduciblity and correctness,
there are some problems with hosted code as well.
The most important one is that hosted code needs maintanance:
the libraries that are used by an experiment
will change over time, inevitably causing the experiment to fail
over time. 
The degradation of software is a known feature for nearly 
four decades (see the definition of 'bit rot' at \cite{steele1983hacker}),
here a more modern (and in this context superior)
definition is used: software collapse \cite{hinsen2019dealing},
in which software fails due to dependencies on other 
software.
Where that paper recommends using older software foundations 
with multiple implementations \cite{hinsen2019dealing},
this paper recommends a modern solution that potentially has more longevity:
to publish the code installed in a virtual environment
(including the dependencies used at that time), as described below.
